Phylogenetics and the human microbiome.

### 2013-09-12 sbreview.tex
fungi in the gut
more refs
abstract tweaks

The human microbiome is the collection of microbes that live inside of and on the outside of humans.
The Human Microbiome Project (HMP) and the Metagenomics of the Human Intestinal Tract (MetaHIT) consortia have advanced human microboime research by generating thousands of 16s surveys and terabases of metagenomic data on the human microbiome, as well as funding bioinformatics and statistical development.
In this paper I review the impact of phylogenetics and tree-thinking on the methods used in the analysis of this data, as well as describing current challenges for phylogenetics coming from this type of work.

@@

@@

So far we have been focusing on bacteria, though archaea also play a role.
Archaea have also been found in the gut.

>>>>

The human microbiome is the collection of microbes that live inside and on the outside of humans.
Recent work including the Human Microbiome Project (HMP) and the Metagenomics of the Human Intestinal Tract (MetaHIT) consortia has advanced human microboime research by generating thousands of 16s surveys and terabases of metagenomic data on the human microbiome.
In this paper I review the impact of phylogenetics and tree-thinking on the methods used in the analysis of human microbiome data, as well as describing current challenges for phylogenetics coming from this type of work.

@@

more virome
http://www.pnas.org/content/early/2013/07/03/1300833110.short
review paper:http://genomebiology.com/2013/14/7/127

mycobiome
http://genomemedicine.com/content/5/7/63

@@

So far we have been focusing on bacteria, though archaea also play a role.
Archaea have also been found in the gut.
and fungi too
http://www.plosone.org/article/info%3Adoi%2F10.1371%2Fjournal.pone.0066019
